Revealing Benefits, Costs, and Tradeoffs of Spatial Management in Marine Systems Arrising from Coupled Economic and Ecological Dynamics

### 2023-05-23 03_marlin_paper.qmd
Fandf (#9)
* initial fandf submission
Slides (#10)
* stopping slides branch 
* use     embed-resources: true to generate shareeable html files
* first real draft of tunacamp presentation

---
format:
  pdf:
    toc: false
    fig-pos: 'H'
    mainfont: Times New Roman
    sansfont: Times New Roman
    fontsize: 12pt
  html: default
  docx: default
execute:
  echo: false
  message: false
  warning: false
  cache: false
csl: apa-6th-edition.csl
bibliography: references.bib
params:
  run_name: ["v1.0"]
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
  - \usepackage{bm}
---

<!-- referees -->

<!-- Maya Tolstoy -->

<!-- Mikaela Provost -->

<!-- Leah Gerber -->

<!-- David M. Kaplan -->

>>>>

---
format:
  pdf:
    toc: false
    fig-pos: 'H'
    mainfont: Times New Roman
    sansfont: Times New Roman
    fontsize: 12pt
    keep-tex: true
    fig-format: png
  html: default
  docx: default
execute:
  echo: false
  message: false
  warning: false
  cache: false
csl: apa-6th-edition.csl
bibliography: references.bib
params:
  run_name: ["v1.0"]
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
  - \usepackage{bm}
---
